### 2018-06-15 papers/synth/intro.tex
qwe
reply

%
VTSs are regulated by the same molecules that they transport.
%
For the purpose of this paper, the VTS molecules we focus on are the transmembrane SNARE proteins.
%
SNAREs drive the recognition of the target compartment by vesicles and
their subsequent fusion.
%
The SNAREs can be divided into v-SNAREs (which are present
on vesicles) and t-SNAREs (which are present on compartments). A
vesicle fuses with a compartment if its v-SNARE can form a complex
with the t-SNARE present on that compartment.
%
Not all v- and t- SNARE combinations can form complexes; this
constraint forms part of the basis for the specificity of vesicle
traffic~\cite{jahn2006snares}.
%
The activity of SNARE proteins is further regulated by their
interaction with other traffic molecules \ashu{ [do we need the following], such as SM
proteins~\cite{sudhof2009membrane} and proteins of tethering
complexes~\cite{hong2014tethering}.}
%

>>>>

%
VTSs are regulated by the same molecules that they transport.
%
For the purpose of this paper, the VTS molecules we focus on are the transmembrane SNARE proteins.
%
SNAREs drive the recognition of the target compartment by vesicles and
their subsequent fusion.
%
The SNAREs can be divided into v-SNAREs (which are present
on vesicles) and t-SNAREs (which are present on compartments). A
vesicle fuses with a compartment if its v-SNARE can form a complex
with the t-SNARE present on that compartment.
%
Not all v- and t- SNARE combinations can form complexes; this
constraint forms part of the basis for the specificity of vesicle
traffic~\cite{jahn2006snares}.
%
The activity of SNARE proteins is further regulated by their
interaction with other traffic molecules \ashu{ [do we need the following], such as SM
proteins~\cite{sudhof2009membrane} and proteins of tethering
complexes~\cite{hong2014tethering}. }
\ankit{From our papers prospective NO. But Biologically Yes. Mukund have written this earlier then stated that "In this paper we focus only on SNARE's ... But somya has did this in reverse. Similar was the case many places, a few of which I fixed. I can give one more try."}
%
